Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-10 TACAS2018/paper.tex
+ comments in observer paper

Since we are interested in synthesising controllers with observer
designs, in this section we will look at checking stability, safety
and the response time in the presence of an observer. A full description of
the theory related to the observer design is provided in appendix \ref{sec:control_theory}

@@

>>>>

Since we are interested in synthesising controllers with observer
designs, in this section we will look at checking stability, safety
and the response time in the presence of an observer. A full description of
the theory related to the observer design is provided in appendix \ref{sec:control_theory}.

@@

\todo{Start by saying what stability means and that we must have the eigenalues
  inside the unity circle and that we want to use Jury's criterion.
  Then, explain what the challenges are for observed systems and how they are overcome. Potentially, the overcoming can be moved to appendix.}
